Notes on Control Plane Inference

### 2021-03-27 inference.tex
attempt with choose; need lexical scope

\usepackage{amsmath, amssymb, amsthm, array, stmaryrd}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{float}
%% \usepackage[notext,not1,nomath]{stix}
\usepackage{enumitem}

@@

% semantics
\newcommand{\pkt}{\mathit{pkt}}
\newcommand{\denote}[1]{\llbracket#1\rrbracket}
\newcommand{\edenote}[1]{\mathcal{E}\denote{#1}}

@@

% commands
\newcommand{\assert}{\mathop{\mathsf{assert}}}
\newcommand{\assume}{\mathop{\mathsf{assume}}}
\newcommand{\apply}{\mathsf{apply}}
\newcommand{\choice}{\mathbin{\rotatebox[origin=c]{90}{$\sqsubset\!\!\!\sqsupset$}}}
\newcommand{\SKIP}{\mathsf{skip}}

%math
\newcommand{\argmin}{\mathop{\textrm{argmin}}}

@@

\begin{figure}[htp]
  \[\begin{array}{lcll}
    \multicolumn{3}{l}{\Value} \\
    v & ::= & [n]_w  & \textit{Bitvector Literal}\\
    \multicolumn{3}{l}{\SymbRow} \\
    \rho & ::= & \left\{
    \begin{array}{l}
      \matches = \List[x];\\
      \action = x;\\
      \data = \List[x]
    \end{array}\right\} & \textit{Symbolic Row}\\
    \multicolumn{3}{l}{\BVExpr} \\
    e & ::= & v & \textit{Value}\\
      & \mid & h.f & \textit{Header Access} \\
      & \mid & \rho.\matches[i] & \textit{Symbolic Match} \\
      & \mid & \rho.\action & \textit{Symbolic Action}\\
      & \mid & \rho.\data[i] & \textit{Symbolic Action Data}\\
      & \mid & x & \textit{Variable}\\
      & \mid & e \binop e & \textit{Arbitrary Binary Operation}\\
    & \mid & \unop e & \textit{Arbitrary Unary Operation}\\
    \multicolumn{3}{l}{\Table} \\
    t & ::= & \left\{\begin{array}{l}
    t.\id = v; \\
    t.\keys = \List[h.f]; \\
    t.\actions = \List[\lambda \vec x. c]\\
    \end{array}\right\} & \textit{Table}\\
    \multicolumn{3}{l}{\BExpr} \\
    b & ::= & \FALSE  & \textit{Falsity}\\
      & \mid & b \Rightarrow b & \textit{Implication} \\
      & \mid & e = e & \textit{Bitvector Equality}\\
    & \mid & \forall \rho \in t.~b & \textit{Row Universality}\\
    \multicolumn{3}{l}{\Cmd} \\
    c & ::=  & h.f := e & \textit{Assignment}\\
      & \mid & \assert b & \textit{Assertion}\\
      & \mid & \assume b & \textit{Assumption}\\
      & \mid & t.\apply() & \textit{Table Application}\\
      & \mid & c;c & \textit{Sequential Composition} \\
    & \mid & c \choice c & \textit{Nondeterministic Choice}\\
    \multicolumn{3}{l}{
      \begin{array}{ll}
        x \in \Var & h \in \Hdr\\
        n,w,i \in \mathbb{N} & f \in \Field
    \end{array}} & \textit{Sets }\\
  \end{array}
\]
\caption{Grammar of Dataplane Programs}
\label{fig:grammar}
\end{figure}

@@

\paragraph{Commands}
Data plane programs $c \in \mathsf{Cmd}$ can be assignments ($h.f := e$),
assumptions ($\assume b$), assertions ($\assert b$), table application
($t.\apply()$), sequential composition ($c_1;c_2$ for two commands $c_1$ and
$c_2$), and nondeterministic choice ($c_1 \choice c_2$ for two commands $c_1$
and $c_2$).

@@

@@

@@

\begin{figure}[htp]
  \[\begin{array}{l>{\triangleq}cl}
  \multicolumn{3}{l}{\edenote{e} : \Pkt \to \Model \rightharpoonup \Value }\\
    \edenote{v}~\pkt~\mu &&
    v \\
    \edenote{h.f}~\pkt~\mu &&
    pkt(h.f)\\
    \edenote{\rho.\matches[i]}~\pkt~\mu &&
    \mu(\rho).\matches[i] \\
    \edenote{\rho.\action}~\pkt~\mu &&
    \mu(\rho).\action \\
    \edenote{\rho.\data[i]} &&
    \mu(\rho).\data[i]\\
    \edenote{e_1 \binop e_2}~\pkt~\mu&&
    \edenote{e_1}~\pkt~\mu \binop
    \edenote{e_2}~\pkt~\mu \\
    \edenote{\unop e}~\pkt~\mu &&
    \unop \left(\edenote{e}~\pkt~\mu\right)
  \end{array}
  \]
  \caption{Semantics of Expressions}
  \label{fig:sem-expr}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{l>{\iff}cl}
  \pkt,\mu \models_\sigma \FALSE && \textit{pigs fly} \\
  \pkt,\mu \models_\sigma b_1 \Rightarrow b_2 &&
  \pkt,\mu \not\models_\sigma b_1~\textit{or}~
  \pkt,\mu \models_\sigma b_2\\
  \pkt,\mu \models_\sigma e_1 = e_2 &&
  \edenote{e_1}~\pkt = \edenote{e_2}~\pkt, \qquad
  \text{(note strict semantics)} \\
  \pkt,\sigma \models \edenote{\forall \rho \in t. b} &&
  \forall r \in \sigma(t.\id).
  \pkt,\sigma,\mu[\rho \mapsto r] \models b
  \end{array}
  \]
  \caption{Satisfaction for $\BExpr$. Write $\pkt \models_\sigma b$ as syntactic
    sugar when the model $\mu$ is empty.}
  \label{fig:bool-satis}
\end{figure}

@@

\begin{figure}[htp]
  \[\begin{array}{l >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c} : \Pkt \to 2^\Pkt_\bot }\\
    \denote{h.f := e}^\sigma~\pkt && \{\pkt\{h \mapsto \edenote{e}\pkt\}\} \\
    \denote{\assume b}^\sigma~\pkt &&
    \begin{cases}
      \{\pkt\} & \pkt \models_\sigma b \\
      \{\} & \textit{otherwise} \\
    \end{cases}\\
    \denote{\assert b}^\sigma \pkt &&
    \begin{cases}
      \{pkt\} & \pkt \models_\sigma b \\
      \bot & \textit{otherwise}
    \end{cases} \\
    \denote{c_1;c_2}^\sigma \pkt&&
    \bigcup_{\pkt' \in \denote{c_1}\pkt}\denote{c_2}~\pkt' \\
    \denote{c_1 \choice c_2}^\sigma \pkt &&
    \denote{c_1}^\sigma~\pkt \cup \denote{c_2}^\sigma~\pkt \\
    \denote{t.\apply()}^\sigma \pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma~\pkt,
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~r = \argmin_i\{\pkt \models_\sigma \sigma(t.\id)[i].\matches = t.\keys \} \\

      \{\pkt\}, & \mathit{otherwise}
    \end{cases}

  \end{array}\]
  \caption{Semantics of Commands}
  \label{fig:com-sem}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{r>{\triangleq}cl}
  (h.f := e)[\sigma] && h.f := e   \\
  (\assume b)[\sigma] && \assume b \\
  (\assert b)[\sigma] && \assert b \\
  (c_1;c_2)[\sigma] && c_1[\sigma];c_2[\sigma] \\
  (c_1 \choice c_2)[\sigma] && c_1[\sigma] \choice c_2[\sigma] \\
  (t.\apply())[\sigma] &&
  \begin{array}[t]{l}
    \{\\
    \quad \assume {r_1.\matches = t.\keys};\\
    \quad t.\action[r_1.\action](r_1.\data)\\
    \}~\choice\\
    \multicolumn{1}{c}{\vdots}\\
    \choice~\{\\
    \quad \assume {r_n.\matches = t.\keys};\\
    \quad t.\action[r_n.\action](r_n.\data)\\
    \}\\
    \textrm{where}~[r_1;\ldots;r_n] = \sigma(t.\id)
  \end{array}
  \end{array}
  \]
  \caption{Table Elimination}
  \label{fig:table-elim}
\end{figure}

\begin{theorem}[Table Elimination]
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$,
  and packet $\pkt \in \Pkt$, then for any state $\tau : \Value \to \Row^*$,
  \[\denote{c}^\sigma~\pkt = \denote{c[\sigma]}^\tau~\pkt\]
\end{theorem}
\begin{proof}
\todo[inline]{By induction on the structure of $c$.}
\end{proof}

@@

\begin{figure}[htp]
  \[\begin{array}{r >{\triangleq}cl}
  (h.f := e)[?] && h.f := e \\
  (\assume b)[?] && \assume b \\
  (\assert b)[?] && \assert b\\
  (c_1;c_2)[?] && c_1[?];c_2[?]\\
  (c_1 \choice c_2)[?] && c_1[?] \choice c_2[?]\\
  (t.\apply())[?] &&
  \begin{array}[t]{l}
  \{ \\
  \quad \assume \rho.\matches = t.\keys; \\
  \quad \{\assume \rho.\action = 0; t.\action[0](\rho.\data)\}\\
  \quad \choice \cdots \\
  \quad \choice \{\assume \rho.action = |t.\action| - 1; t.\action[t.\action - 1](\rho.\data)\}\\
  \quad \}\\
  \} \choice \{ \\
  \quad \assume \forall \rho \in t. \rho.\matches \neq t.\keys; \\
  \quad \SKIP \\
  \quad \}\\
  \}
  \end{array}
  \end{array}
  \]
\end{figure}

\todo[inline]{This is wrong because $\rho$ is unbound in the first branch}

\begin{theorem}[Instrumentation Sufficiency]
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, and
  packet $\pkt \in \Pkt$, $\denote{c}^\sigma~\pkt = \pkt'$ if and only if
  $\pkt' \in \denote{c[?]}^\sigma~\pkt$
\end{theorem}

\begin{proof}
\todo[inline]{By induction on the structure of $c$}
\end{proof}

>>>>

\usepackage{amsmath, amssymb, amsthm, array, stmaryrd}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{float}
\usepackage{scalerel}
%% \usepackage[notext,not1,nomath]{stix}
\usepackage{enumitem}

@@

% semantics
\newcommand{\pkt}{\mathit{pkt}}
\newcommand{\error}{\mathsf{error}}
\newcommand{\denote}[1]{\left\llbracket#1\right\rrbracket}
\newcommand{\edenote}[1]{\mathcal{E}\denote{#1}}

@@

% commands
\newcommand{\assert}{\mathop{\mathsf{assert}}}
\newcommand{\assume}{\mathop{\mathsf{assume}}}
\newcommand{\apply}{\mathsf{apply}}
\newcommand{\choiceop}{\rotatebox[origin=c]{90}{$\sqsubset\!\!\!\sqsupset$}}
\newcommand{\choice}{\mathbin{\choiceop}}
\DeclareMathOperator*{\bigchoice}{\scalerel*{\choiceop}{\sum}}
\renewcommand{\choose}[2]{\mathsf{choose}~#1~\mathsf{from}~#2}
\newcommand{\SKIP}{\mathsf{skip}}

% math
\newcommand{\argmin}{\mathop{\textrm{argmin}}}

% defined functions
\newcommand{\tables}{\mathop{\mathsf{tables}}}

@@

\begin{figure}[htp]
  \[\begin{array}{lcll}
    \multicolumn{3}{l}{\Value} \\
    v & ::= & [n]_w  & \textit{Bitvector Literal}\\
    \multicolumn{3}{l}{\SymbRow} \\
    \rho & ::= & \left\{
    \begin{array}{l}
      \matches = \List[x];\\
      \action = x;\\
      \data = \List[x]
    \end{array}\right\} & \textit{Symbolic Row}\\
    \multicolumn{3}{l}{\BVExpr} \\
    e & ::= & v & \textit{Value}\\
      & \mid & h.f & \textit{Header Access} \\
      & \mid & \rho.\matches[i] & \textit{Symbolic Match} \\
      & \mid & \rho.\action & \textit{Symbolic Action}\\
      & \mid & \rho.\data[i] & \textit{Symbolic Action Data}\\
      & \mid & x & \textit{Variable}\\
      & \mid & e \binop e & \textit{Arbitrary Binary Operation}\\
    & \mid & \unop e & \textit{Arbitrary Unary Operation}\\
    \multicolumn{3}{l}{\Table} \\
    t & ::= & \left\{\begin{array}{l}
    t.\id = v; \\
    t.\keys = \List[h.f]; \\
    t.\actions = \List[\lambda \vec x. c]\\
    \end{array}\right\} & \textit{Table}\\
    \multicolumn{3}{l}{\BExpr} \\
    b & ::= & \FALSE  & \textit{Falsity}\\
      & \mid & b \Rightarrow b & \textit{Implication} \\
      & \mid & e = e & \textit{Bitvector Equality}\\
    & \mid & \forall \rho \in t.~b & \textit{Row Universality}\\
    \multicolumn{3}{l}{\Cmd} \\
    c & ::=  & h.f := e & \textit{Assignment}\\
      & \mid & \assert b & \textit{Assertion}\\
      & \mid & \assume b & \textit{Assumption}\\
      & \mid & \choose \rho t & \textit{Selection} \\
      & \mid & t.\apply() & \textit{Table Application}\\
      & \mid & c;c & \textit{Sequential Composition} \\
    & \mid & c \choice c & \textit{Nondeterministic Choice}\\
    \multicolumn{3}{l}{
      \begin{array}{ll}
        x \in \Var & h \in \Hdr\\
        n,w,i \in \mathbb{N} & f \in \Field
    \end{array}} & \textit{Sets }\\
  \end{array}
\]
\caption{Grammar of Dataplane Programs}
\label{fig:grammar}
\end{figure}

@@

\paragraph{Commands}
Data plane programs $c \in \mathsf{Cmd}$ can be assignments ($h.f := e$),
assumptions ($\assume b$), assertions ($\assert b$), table application
($t.\apply()$), nondeterministic selection ($\choose \rho t$), sequential composition ($c_1;c_2$ for two commands $c_1$ and
$c_2$), and nondeterministic choice ($c_1 \choice c_2$ for two commands $c_1$
and $c_2$).

@@

Define $\tables(c) \subset \Table$ to be the set of all tables hat occur in $c$.

@@

A state map $\sigma : \Value \to \Row^*$ is well-formed for a command $c$ iff the
following conditions hold:
\begin{enumerate}
\item[\textsc{WellFormedRows}] For every $t\in \tables(c)$, every row in $\sigma(t.\id)$ is well-formed.
\item[\textsc{NoShadow}] For every $t \in \tables(c)$, with $r_1,\ldots,r_n =
  \sigma(t.\id)$, for every $1 \leq i \leq n$, there does not exist $1 \leq j <
  i$ such that $r_i.\matches = r_j.\matches$.
\end{enumerate}
\todo[inline]{Tables(c) is undefined}

@@

\begin{figure}[H]
  \[\begin{array}{l>{\triangleq}cl}
  \multicolumn{3}{l}{\edenote{e} : \Pkt \to \Model \rightharpoonup \Value }\\
    \edenote{v}~\pkt~\mu &&
    v \\
    \edenote{h.f}~\pkt~\mu &&
    pkt(h.f)\\
    \edenote{\rho.\matches[i]}~\pkt~\mu &&
    \mu(\rho).\matches[i] \\
    \edenote{\rho.\action}~\pkt~\mu &&
    \mu(\rho).\action \\
    \edenote{\rho.\data[i]} &&
    \mu(\rho).\data[i]\\
    \edenote{e_1 \binop e_2}~\pkt~\mu&&
    \edenote{e_1}~\pkt~\mu \binop
    \edenote{e_2}~\pkt~\mu \\
    \edenote{\unop e}~\pkt~\mu &&
    \unop \left(\edenote{e}~\pkt~\mu\right)
  \end{array}
  \]
  \caption{Semantics of Expressions}
  \label{fig:sem-expr}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{l>{\iff}cl}
  \pkt,\mu \models_\sigma \FALSE && \textit{pigs fly} \\
  \pkt,\mu \models_\sigma b_1 \Rightarrow b_2 &&
  \pkt,\mu \not\models_\sigma b_1~\textit{or}~
  \pkt,\mu \models_\sigma b_2\\
  \pkt,\mu \models_\sigma e_1 = e_2 &&
  \edenote{e_1}~\pkt~\mu = \edenote{e_2}~\pkt~\mu, \qquad
  \text{(note strict semantics)} \\
  \pkt,\mu \models_\sigma \forall \rho \in t. ~b &&
  \forall r \in \sigma(t.\id).
  \pkt,\sigma,\mu[\rho \mapsto r] \models b
  \end{array}
  \]
  \caption{Satisfaction for $\BExpr$. Write $\pkt \models_\sigma b$ as syntactic
    sugar when the model $\mu$ is empty.}
  \label{fig:bool-satis}
\end{figure}

@@

\begin{figure}[htp]
  \[\begin{array}{l >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c}^\sigma : \Model \to \Pkt \to \mathcal{P}(\Model \times \Pkt)_\error }\\
    \denote{h.f := e}^\sigma~\mu~\pkt && \{(\mu, \pkt\{h \mapsto \edenote{e}~\pkt~\mu\})\} \\
    \denote{\assume b}^\sigma~\mu~\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \pkt,\mu \models_\sigma b \\
      \{\} & \textit{otherwise} \\
    \end{cases}\\
    \denote{\assert b}^\sigma~\mu~\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \pkt,\mu \models_\sigma b \\
      \error & \textit{otherwise}
    \end{cases} \\
    \denote{\choose \rho t}^\sigma~\mu~\pkt &&
    \bigcup_{r \in \sigma(t)}\{(\pkt,\mu\{\rho \mapsto r\})\}
    \\
    \denote{c_1;c_2}^\sigma~\mu~\pkt&&
    \bigcup_{(\mu',\pkt') \in \denote{c_1}^\sigma\,\mu\,\pkt}\denote{c_2}^\sigma~\mu'~\pkt' \\
    \denote{c_1 \choice c_2}^\sigma~\mu~\pkt &&
    \denote{c_1}^\sigma~\mu~\pkt \cup \denote{c_2}^\sigma~\mu~\pkt \\
    \denote{t.\apply()}^\sigma~\mu~\pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma~\mu~\pkt,
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~r = \argmin_i\{\pkt,\mu \models_\sigma \sigma(t.\id)[i].\matches = t.\keys \} \\
      \{(\mu,\pkt)\}, & \mathit{otherwise}
    \end{cases}
  \end{array}\]
  \caption{Semantics of Commands}
  \label{fig:com-sem}
  \todo[inline]{$\Model$ then $\Pkt$ everywhere.}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{r>{\triangleq}cl}
  (h.f := e)[\sigma] && h.f := e   \\
  (\assume b)[\sigma] && \assume b \\
  (\assert b)[\sigma] && \assert b \\
  (c_1;c_2)[\sigma] && c_1[\sigma];c_2[\sigma] \\
  (c_1 \choice c_2)[\sigma] && c_1[\sigma] \choice c_2[\sigma] \\
  (\choose \rho t)[\sigma] && \textrm{\textcolor{red}{unnecessary, but similar to t.apply}}\\
  (t.\apply())[\sigma] &&
  \begin{array}[t]{l}
    \{\\
    \quad \assume {r_1.\matches = t.\keys};\\
    \quad t.\action[r_1.\action](r_1.\data)\\
    \}~\choice\\
    \multicolumn{1}{c}{\vdots}\\
    \choice~\{\\
    \quad \assume {r_n.\matches = t.\keys};\\
    \quad t.\action[r_n.\action](r_n.\data)\\
    \}\\
    \textrm{where}~[r_1;\ldots;r_n] = \sigma(t.\id)
  \end{array}
  \end{array}
  \]
  \caption{Table Elimination}
  \label{fig:table-elim}
\end{figure}

\begin{theorem}[Table Elimination]
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, model
  $\mu \in \Model$, and packet $\pkt \in \Pkt$, then for any state $\tau :
  \Value \to \Row^*$,
  \[\denote{c}^\sigma~\mu~\pkt = \denote{c[\sigma]}^\tau~\mu~\pkt\]
\end{theorem}
\begin{proof}
\todo[inline]{By induction on the structure of $c$.}
\end{proof}

@@

\begin{figure}[htp]
  \[\begin{array}{r >{\triangleq}cl}
  (h.f := e)[?] && h.f := e \\
  (\assume b)[?] && \assume b \\
  (\assert b)[?] && \assert b\\
  (c_1;c_2)[?] && c_1[?];c_2[?]\\
  (c_1 \choice c_2)[?] && c_1[?] \choice c_2[?]\\
  (\choose \rho t)[?] &&
  \textrm{\textcolor{red}{unnecessary}} \\
  (t.\apply())[?] &&
  \begin{array}[t]{l} \displaystyle
    \{ \\
    \quad \choose \rho t; \\
    \quad \assume \rho.\matches = t.\keys; \\
    \quad \displaystyle \bigchoice_{i=0}^{|t.\action| -1}
    \left\{\begin{array}{l}
    \assume \rho.\action = i;\\
    t.\action[i](\rho.\data)
    \end{array}\right\}\\
    \} \choice \{ \\
    \quad \assume \forall \rho \in t. \rho.\matches \neq t.\keys; \\
    \quad \SKIP \\
    \quad \}\\
    \}
  \end{array}
  \end{array}
  \]
  \caption{Symbolic Table instrumentation}
  \label{fig:table-instrument}
\end{figure}

\begin{theorem}[Instrumentation Expressivity]
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, model
  $\mu \in \Model$, and packet $\pkt \in \Pkt$, $\denote{c}^\sigma~\mu~\pkt =
  \denote{c[?]}^\sigma~\mu~\pkt$.
\end{theorem}

\begin{proof}
  Proceed by induction on the structure of $c$, leaving $\sigma$, $\mu$, $\pkt$ general.
  \begin{enumerate}[align=left]
  \item[$(c = h.f := e)$]
    Let $\sigma$,$\mu$,$\pkt$ be given.
    By definition $h.f:=e[?] = h.f:=e$. The result follows.
  \item[$(c = \assume b)$] Similar. $[?]$ is no-op.
  \item[$(c = \assert b)$] Similar. $[?]$ is no-op.
  \item[$(c = \choose \rho t)$] \textcolor{red}{Admitted}.
  \item[$(c = c_1;c_2)$]
    Let $\sigma,\mu,\pkt$ be given.
    By definition $(c_1;c_2)[?] = c_1[?]; c_2[?]$.
    Compute as follows:
    \[\begin{array}{>{\displaystyle}ll}
    \denote{(c_1;c_2)[?]}^\sigma~\mu~\pkt \\
    = \denote{c_1[?];c_2[?]}^\sigma~\mu\pkt
    & \text{by definition of } [?]  \\
    = \bigcup_{(\mu',\pkt') \in \denote{c_1[?]}^\sigma\,\mu\,\pkt}\denote{c_2[?]}^\sigma~\mu'~\pkt'
    & \text{by definition of }\denote{-} \\
    = \bigcup_{(\mu',\pkt') \in \denote{c_1}^\sigma\,\mu\,\pkt}\denote{c_2[?]}^\sigma~\mu'~\pkt'
    & \text{by } \mathit{IH}(c_1, \mu, \pkt) \\
    = \bigcup_{(\mu',\pkt') \in \denote{c_1}^\sigma\,\mu\,\pkt}\denote{c_2}^\sigma~\mu'~\pkt'
    & \text{by } \mathit{IH}(c_2, \mu', \pkt') \\
    = \denote{c_1;c_2}^\sigma~\mu~\pkt
    & \text{by definition of } \denote{-}
    \end{array}
    \]
  \item[$(c = c_1 \choice c_2)$] Similar, by IHs.

  \item[$(c = t.\apply())$]
    Let $\sigma$,$\mu$,$\pkt$ be given.
    Let $r_1,\ldots,r_n = \sigma(t)$.
    There are two cases, either the packet hits a row, or hits no row. Explore each case separately.
    \begin{enumerate}
    \item[\textsc{Hit}] In this case, there is some $r_i$ such that $\pkt,\mu
      \models_\sigma r_i.\matches = t.\keys$. By the well-formedness assumption,
      we know that this $r_i$ is unique, and that we can write
      $t.\actions[r_i.\action]$ as $\lambda \vec x. c$, and $|r_i.\data| = |\vec x|$.

      Compute as follows:
      \[\begin{array}{>{\displaystyle}ll}
      \denote{t.\apply()}^\sigma~\mu~\pkt \\
      = \denote{c[r_i.data/\vec x]}^\sigma~\mu~\pkt & \text{by definition of} \models \text{, and the uniqueness of }r_i  \\
      \end{array}
      \]

      Now, we compute the denotation of $t.\apply()[?]$ to see that it is equivalent to the above.
      The definition of $t.\apply()[?]$ gives us two alternatives. Consider the second, first:
      \[\begin{array}{>{\displaystyle}ll}
        \denote{\assume \forall \rho \in t. \rho.\matches \neq t.\keys;\SKIP}^\sigma~\mu~\pkt \\
        = \denote{\assume \forall \rho \in t. \rho.\matches \neq t.\keys}^\sigma~\mu~\pkt
        & \textrm{\textcolor{red}{Redo with defaults}} \\
        = \begin{cases}
          \{(\mu,\pkt)\}, & \pkt,\mu \models_\sigma \rho.\matches \neq t.\keys \\
          \{\}, &\textit{otherwise}
        \end{cases}
        & \textrm{By definition of }\denote{-}\\
        =  \{\}
        & \textrm{by \textsc{Hit} assumption}
      \end{array}
      \]

      Now let's consider the first branch, considering each command sequentially.
      \[\begin{array}{>{\displaystyle}ll}
      \denote{\choose \rho t; \assume \rho.\matches = t.\keys}^\sigma~\mu~\pkt \\
      = \bigcup_{r \in \sigma(t)}\denote{\assume\rho.\matches = t.\keys}^\sigma~\mu\{\rho \mapsto r\}~\pkt
      & \textrm{by definition of }\denote{-}\\
      = \{(\mu\{\rho\mapsto r\},\pkt)
      \mid r \in \sigma(t), \pkt,\mu\{\rho\mapsto r\} \models_\sigma \rho.\matches = t.\keys
      \}
      & \textrm{by definitions and set theory} \\
      = \{(\mu\{\rho \mapsto r\}, \pkt)
      \mid r \in \sigma(t), \pkt,\mu \models_\sigma r.\matches = t.\keys\}
      & \textrm{by definitions \textcolor{red}{TODO Lemma}} \\
      = \{(\mu\{\rho \mapsto r_i\}, \pkt)\}
      & \textrm{by \textsc{Hit} and \textsc{NoShadow}} \\
      \end{array}\]

      Now by the sequential composition rule, we can determine the result of the
      first branch by computing as follows:
      \[\begin{array}{>{\displaystyle}ll}
      \denote{\bigchoice_{i=0}^{|t.\action| -1}
        \left\{\begin{array}{l}
        \assume \rho.\action = i;\\
        t.\actions[i](\rho.\data)
        \end{array}\right\}
      }^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      = \denote{\denote{c[r_i.\data/\vec x]}^\sigma~(\mu\{\rho \mapsto r\})~\pkt}\\
      & \textrm{skipping lots of definition steps} \\
      \end{array}
      \]
      \todo[inline]{Need Scoping Rules for $\rho$}

    \item[\textsc{Miss}]
      \todo[inline]{Should be easy}

    \end{enumerate}

  \end{enumerate}
\end{proof}
